Parsing Tweets into Universal Dependencies

### 2017-11-27 paper.tex
N - worked on intro

\begin{document}
\maketitle
\begin{abstract}
In this paper, we study the problem of analyzing tweets with
universal dependencies \citep[UD]{NIVRE16.348}. We extend the UD guidelines to cover
special constructions in tweets. Under such guidelines, we create
a new tweet treebank ({\sc Tweebank v2}), which has 55,607 tokens with labelled attachments.\yicomment{labelled attachments}
It is more than 4 times larger than the unlabelled {\sc Tweebank v1} \citep{kong-EtAl:2014:EMNLP2014}. \yicomment{unlabelled attachments for the original Tweebank}
We characterize the disagreements
among our annotation and show that it is challenging to deliver
consistent annotation due to the ambiguities in ways of
understanding and explaining the tweets. Over the new treebank,
we build a pipeline system to parse raw tweets into UD. To conquer the
annotation noise without sacrificing efficiency, we propose a new
method to distill an ensemble of 20 parsers into a single one. Our
parser achieves an improvement of 2.3 in LAS over the baseline
and outperforms other state-of-the-art parsers.
\end{abstract}

\section{Introduction}
Analyzing the syntax of tweets is challenging. The challenges not
only come from the difficulty of adapting the parser trained on the
standard text to the Twitter domain, but also comes from creating
reasonable dataset for training and evaluating tweet parsers. 
\citet{AAAIW113912} pioneered in this research direction by
annotating Penn Treebank \citep[PTB]{Marcus93buildinga}
constituencies to a set of tweets which contains 7,630 tokens. 
Stanford dependencies were converted afterwards. 
\citet{kong-EtAl:2014:EMNLP2014} further studied the challenges in
annotating tweets and presented a tweet treebank ({\sc Tweebank})
which has 12,149 tokens and largely followed the conventions
suggested by \citet{schneider-EtAl:2013:LAW7-ID} that are close to 
\citet{Yamada03statisticaldependency} dependencies. 
Both annotation efforts were highly influenced by the PTB, whose guideline
has a good grammatical coverage on newswire. However, when it comes
to the noisy and informal user generated text, it's questionable
whether such good coverage holds.
%Motivation notes:  explain why UD is attractive (and more attractive
%than what previous work used, which was based on YM).  one reason is
%that it might allow sharing of texts annotated in different genres (or
%even languages, cite Waleed).  but universal annotation schemes are
%challenging!  this paper contends with the challenges of
%applying UD to social media texts.

@@

Universal dependencies \citep[UD]{NIVRE16.348} was created to deliver
consistent annotation across different languages. To allow such
consistency, UD was designed to be adaptive to different genres and languages
\cite{guo-EtAl:2015:ACL-IJCNLP2,TACL892}. It's promising that analyzing
the syntax of tweets can benefit from such adaptability. In this paper,
we create a new tweet treebank of 55,607 tokens by following the UD
guidelines but also contending the domain-specific challenges which were not
covered by UD guidelines. Our annotation includes a whole pipeline of
tokenization, part-of-speech (POS) tags and universal dependencies.
We characterize the disagreement among our annotations and show that
consistent annotation is still challenging to deliver even with
the extended guidelines.

@@

Based on these annotations, we built up a whole pipeline to parse the
raw tweet text into universal dependencies. Our pipeline includes: a
bidirectional LSTM (bi-LSTM) tokenizer, a word cluster enhanced POS
tagger \cite{owoputi-EtAl:2013:NAACL-HLT}, and stack-lstm parser
with character representation \cite{ballesteros-dyer-smith:2015:EMNLP}.

To conquer the noise in our annotation and achieve better performance
without sacrificing efficiency, we propose a new method to
train the parser with the distillation 
\cite{DBLP:journals/corr/HintonVD15} of 20 parsers ensemble.
We show that learning from the exploration of the ensemble parser
can be more beneficial than just learning from the gold standard
transition sequence in the sense of training a transition-based
distilling parser. Experimental results show that an improvement of more
than 2.3 points in LAS over baseline parser can be achieved with our
distillation method and it outperforms other state-of-the-art parsers.

Contribution of this paper includes:
\begin{itemize}
\item We studied the challenges of annotating tweets in UD (\S\ref{sec:anno})
and created a new tweet treebank ({\sc Tweebank v2}), which includes 
tokenization, part-of-speech tagging, and dependencies annotation.
We also characterized the difficulties of creating such annotation.

\item We built up a whole pipeline to parse the raw tweet text into
universal dependencies (\S\ref{sec:parsing}). We proposed a new distillation
method in training the parser in our pipeline which achieve 2.3 points improvement in LAS
without sacrificing efficiency and outperformed other state-of-the-art parsers
in our comparison. \yicomment{change verbs to past tense}
\end{itemize}

@@

\nascomment{I didn't do anything significant to the intro.  for every
  example, make clear whether it's ``real'' or contrived.}
\yjcomment{I've add the source of our example in the figure caption.}
\section{Annotation}\label{sec:anno}
\yicomment{Maybe we should contrast UD and kong's annotation strategy during each stage, because UD has also annotation guideline for every stage.}
In this section, we first review {\sc Tweebank v1} of \citet{kong-EtAl:2014:EMNLP2014},
which is the largest twitter dependencies annotation in previous literals (\S\ref{sec:tweebank}).
Then we introduce the difference in our tokenization and part-of-speech (re)annotation with \citet{ICWSM101540} and 
\citet{gimpel-EtAl:2011:ACL-HLT2011} on which {\sc Tweebank v1} was built (\S\ref{sec:pos-anno}). \yicomment{add tok} 
Then, we move to our effort of adopting the
UD conventions to cover tweet specific constructions. 
At last, we describe our process of creating new tweet treebank and characterize
the difficulties in reaching consistent annotations.
\nascomment{need to introduce this section and explain the structure.}
\yjcomment{done.}

>>>>

\begin{document}
\maketitle
\begin{abstract}
We study the problem of analyzing tweets with
universal dependencies \citep[UD;][]{NIVRE16.348}. We extend the UD guidelines to cover
special constructions in tweets. Using the extended guidelines, we create
a new tweet treebank ({\sc Tweebank v2}), which has 55,607 tokens with
labeled attachments. 
It is more than four times larger than the (unlabeled) {\sc Tweebank
  v1} introduced by \citet{kong-EtAl:2014:EMNLP2014}. 
We characterize the disagreements
among our annotation and show that it is challenging to deliver
consistent annotation due to ambiguity in
understanding and explaining tweets. Using the new treebank,
we build a pipeline system to parse raw tweets into UD. To conquer the
annotation noise without sacrificing computational efficiency, we propose a new
method to distill an ensemble of 20 parsers into a single one. Our
parser achieves an improvement of 2.3 in LAS over \nascomment{which?} the baseline
and outperforms parsers that are state-of-the-art on other treebanks.
\end{abstract}

\section{Introduction}
NLP for social media messages is challenging, both because domain
adaptation is required, but also because creating annotated datasets
(e.g., treebanks)
for training and evaluation is hard. 
Pioneering work by \citet{AAAIW113912} 
annotated 7,630 tokens' worth of tweets according to the
phrase-structure conventions of the Penn Treebank \citep[PTB]{Marcus93buildinga}.
Stanford dependencies were converted afterwards \nascomment{by who?}. 
\citet{kong-EtAl:2014:EMNLP2014} further studied the challenges in
annotating tweets and presented a tweet treebank ({\sc Tweebank}),
consisting of 12,149 tokens and largely following conventions
suggested by \citet{schneider-EtAl:2013:LAW7-ID}, fairly close to 
\citet{Yamada03statisticaldependency} dependencies (without labels). 
Both annotation efforts were highly influenced by the PTB, whose guidelines
have  good grammatical coverage on newswire. However, when it comes
to informal, unedited, user-generated text, the guidelines may leave
many annotation decisions unspecified.
%Motivation notes:  explain why UD is attractive (and more attractive
%than what previous work used, which was based on YM).  one reason is
%that it might allow sharing of texts annotated in different genres (or
%even languages, cite Waleed).  but universal annotation schemes are
%challenging!  this paper contends with the challenges of
%applying UD to social media texts.

@@

Universal dependencies \citep[UD]{NIVRE16.348} were introduced to enable
consistent annotation across different languages. To allow such
consistency, UD was designed to be adaptable to different genres and languages
\cite{guo-EtAl:2015:ACL-IJCNLP2,TACL892}. We propose that analyzing
the syntax of tweets can benefit from such adaptability. In this paper,
we introduce a new tweet treebank of 55,607 tokens that follows the UD
guidelines, but also contends with social media-specific challenges that were not
covered by UD guidelines. Our annotation includes 
tokenization, part-of-speech (POS) tags, and (labeled) universal dependencies.
We characterize the disagreement among our annotations and find that
consistent annotation is still challenging to deliver even with
the extended guidelines.

@@

Based on these annotations, we designed a pipeline to parse 
raw tweets into universal dependencies. Our pipeline includes: a
bidirectional LSTM (bi-LSTM) tokenizer, a word cluster-enhanced POS
tagger \citep[following][]{owoputi-EtAl:2013:NAACL-HLT}, and a stack LSTM parser
with character-based word representations
\cite{ballesteros-dyer-smith:2015:EMNLP}, which we refer to as our
``baseline'' parser.

To overcome the noise in our annotated data and achieve better performance
without sacrificing computational efficiency, we propose a new method to
train the parser with the distillation 
\cite{DBLP:journals/corr/HintonVD15} of a 20-parser
ensemble. \nascomment{return to this and clarify}
We show that learning from the exploration of the ensemble parser
can be more beneficial than just learning from the gold standard
transition sequence in the sense of training a transition-based
distilling parser. Experimental results show that an improvement of more
than 2.3 points in LAS over the baseline parser can be achieved with our
distillation method and it outperforms other state-of-the-art parsers.

The contributions of this paper include:
\begin{itemize}
\item We study the challenges of annotating tweets in UD (\S\ref{sec:anno})
and created a new tweet treebank ({\sc Tweebank v2}), which includes 
tokenization, part-of-speech tagging, and labeled universal dependencies annotation.
We also characterize the difficulties of creating such annotation.

\item We introduce and evaluate a system to parse the raw tweet text into
universal dependencies (\S\ref{sec:parsing}).  \nascomment{say it
  performs better than existing systems?}
\item We propose a new distillation
method for training the parser in our pipeline,  which achieves 2.3 points improvement in LAS
without sacrificing efficiency and outperformed other state-of-the-art parsers
in our comparison. \nascomment{clean up, remove redundancies with
  previous paragraph}
\end{itemize}

@@

\yjcomment{I've add the source of our example in the figure caption.}
\section{Annotation}\label{sec:anno}
\yicomment{Maybe we should contrast UD and kong's annotation strategy during each stage, because UD has also annotation guideline for every stage.}
In this section, we first review {\sc Tweebank v1} of \citet{kong-EtAl:2014:EMNLP2014},
which is the largest twitter dependencies annotation in previous literals (\S\ref{sec:tweebank}).
Then we introduce the difference in our tokenization and part-of-speech (re)annotation with \citet{ICWSM101540} and 
\citet{gimpel-EtAl:2011:ACL-HLT2011} on which {\sc Tweebank v1} was built (\S\ref{sec:pos-anno}). \yicomment{add tok} 
Then, we move to our effort of adopting the
UD conventions to cover tweet specific constructions. 
At last, we describe our process of creating new tweet treebank and characterize
the difficulties in reaching consistent annotations.
\nascomment{need to introduce this section and explain the structure.}
\yjcomment{done.}
